\section{Group Members Contribution}

% For each group member, describe in detail the contribution to the project.

\begin{description}
	\item[Manuel Antonutti] contributed to this project by:
		\begin{enumerate}
			\item Helping in the ER schema development for the database.
			\item Creating the mock up for the Cart and PreviousOrders pages in the customer view.
			\item Creating the FullDish and FullOrder classes in the \textit{dbentities} folder.
			\item Implementing the ListDishesFromOrder RR and DAO classes.
			\item Implementing the ListPreviousOrders RR and DAO classes.
			\item Implementing the AddDishToOrder RR and DAO classes.
			\item Implementing the UpdateDishQuantity RR and DAO classes.
			\item Implementing the DeleteDishFromOrder RR and DAO classes.
			\item Implementing the DeleteAllDishesFromOrder RR and DAO classes.
			\item Implementing the CompleteOrder RR and DAO classes.
			\item Implementing all the SQL procedures and functions in \textit{festival-query.sql} for the DAOs above.
			\item Providing the class diagrams for the project.
			\item Providing the sequence diagrams for the project.
		\end{enumerate}
	\item[Daniel Carlesso] contributed to this project by :
            \begin{enumerate}
                \item Helping in the ER schema development and doing the implementation.
                \item Implementing the initialization of the db and the queries (not all).
                \item Helping with the mocking in general and focusing more on the user functionalities.
                \item Implementing the Login/Register/Logout RR and DAO + PasswordGenerator class.
                \item Implementing the UpdateUser/DeleteUser RR and DAO.
                \item Implementing the CreateRestaurant/DeleteRestaurant RR and DAO.
                \item Implementing the CreateDish/DeleteDish RR and DAO.
                \item Implementing the resource filters + JWT class.
                \item Implementing the following DAOs used by other RR: CreateCuisinesDAO, CreateIngredientsDAO, GetManagerDAO.
                \item Filling DLL in the report.
                \item Filling the admin.tex file for the presentation logic layer.
            \end{enumerate}
	\item[Luigi Frigione] contributed to this project by:
		\begin{enumerate}
			\item Helping in the ER schema development for the database.
			\item Designing and implementing the docker configuration.
			\item Designing and implementing the application database connection with a special user with limited permissions.
			\item Implementing the first version of ListRestaurants API.
			\item Studying and configuring \underline{\href{https://stripe.com/en-it}{Stripe}} integration for online payments.
			\item Implementing list user credit cards API.
			\item Designing payment API but not implementing it yet since stripe JavaScript library is needed.
			\item Modifying user register API to be integrated with stripe (on registration we create an associate customer entity on the Stripe ecosystem).
			\item Debugging and solving all the Javadoc errors.
			\item Writing the README.md file of the report with the instructions to build and navigate the application.
			\item Testing the application.
			\item Writing the documentation of the REST API summary in the HW1 report.
			\item Writing the documentation of the REST API details for: restaurant (create, search and delete), cuisine types (list) and order (add, remove, update, remove all, complete, list content, list previous).
		\end{enumerate}
	\item[Mahshid Shams] contributed to this project by:
	\begin{enumerate}
    			\item Participating in the creation of the ER schema database.
    			\item Designing the user experience and creating a mockup for the Figma.
    			\item Designing the mockups for the restaurant and the dish, as well as the admin and manager's view of the figma.
    			\item Implementing the listUserDAO.
    			\item Implementing the listUser Rest API.
    			\item Adding real data to the mockups.
    			\item Writing the documentation of the mockup for Restaurant manager view.
    			\item Writing the documentation of the mockup for Dish manager view.
    		\end{enumerate}
	\item[Nicola Ursino] contributed to this project by:
		\begin{enumerate}
		\item Helping in the ER schema development for the database.
		\item Implementing the logging functionality.
		\item Helping with the mock up in general and focusing more on the searching functionality.		
		\item Creating an initial version of the java classes for each db entity.
		\item Implementing the SearchDishesByRestaurantByNameByDiet REST API and DAO.
		\item Implementing the SearchRestaurantByNameByCuisine REST API and DAO.
		\item Implementing the UpdateUser REST API and DAO.
		\item Implementing the ListUserByEmail REST API and DAO.
		\item Implementing the ListCuisineTypes REST API and DAO useful for the advanced search.
		\item Implementing all (except UpdateUser that had already been implemented by Daniel Carlesso) the SQL functions in \textit{festival-query.sql} for the DAOs above.
		\item Implementing the initial organization of the REST error codes into a java class (RestErrorCodes.java).
		\item Rebuilding  the RestDispatcherServlet.java from scratch.
		\item Writing the User View section for the presentation logic layer.
		\item Writing the documentation of the REST Error Codes for the  business logic layer.
		\item Writing the documentation of the REST API details for: dish (create, search and delete) and user (register, create, update, login, logout, delete, list, search, list cards).
	\end{enumerate}

\end{description}
