\section{Main Functionalities}
%What are the main functionalities of the web app? what services does it offer and how it is organized?

The PL8S web application is designed to provide a way of ordering food from various restaurants at festivals. Its core functionalities include:

\begin{itemize}

	\item Menu Display: The application displays the menus from each restaurant, allowing users to browse through different dishes and their ingredients. This feature is particularly useful for users with specific dietary requirements or allergies, enabling them to make informed choices before placing an order. 

	\item Advanced Search Tool: To enhance the user experience, PL8S offers an advanced search tool that enables users to find specific dishes across all participating restaurants. In this way, the customers can quickly find their favourite dish.
	
	\item Virtual Shopping Cart: Once a user selects a dish, it is added to a virtual shopping cart. This cart allows users to adjust the quantity of each item, remove selected dishes, and view the total bill. This functionality ensures a smooth and efficient ordering process, providing users with full control over their order before finalizing it.
	
	\item User Authentication: Upon launching the web application, users are presented with a login and registration page. This feature allows new users to create an account with a username and a password, which can be modified later. Unregistered or unlogged users are considered as customers and can browse the Customer View without the ability to manage a cart or place orders.

\end{itemize}


